% !TeX root = ../main.tex

\ustcsetup{
  keywords = {
    众包数据交易,区块链,贝叶斯纳什均衡,版权保护
  },
  keywords* = {
    Crowdsourcing data trading,Blockchain,Bayesian Nash equilibrium,Copyright protection
  },
}

\begin{abstract}
%  摘要是论文内容的总结概括，应简要说明论文的研究目的、基本研究内容、 研究方法或
%  过程、结果和结论，突出论文的创新之处。摘要中不宜使用公式、图表，不引用文献。
%  博士论文中文摘要一般800～1000个汉字，硕士论文中文摘要一般600个汉字。英文摘要的
%  篇幅参照中文摘要。

%  关键词另起一行并隔写在摘要下方，一般3～8个词，中文关键词间空一字或用分号“；”隔
%  开。英文摘要的关键词与中文摘要的关键词应完全一致，中间用逗号“,”或分号“;”隔开。
  传统的众包数据交易依赖于可信第三方，而依赖可信第三方既显著提
  高成本又难以防止合谋行为以保证公平性。区块链和智能合约的出现提供
  了一种去中心化的方案来自动化拍卖过程。然而现有的方案无法在择最适
  合的供应商的同时保证交易的真实性和个体理性。为此提出一种利用贝叶斯纳什均衡和
  智能合约技术的拍卖模型。
  首先，使用贝叶斯纳什均衡选出具有最大效益的供应商。
  其次，由于区块链的透明性，为了满足静态贝叶斯纳什均衡的基本假
  设，保证同时出价，提出了一种两阶段的消息提交算法，以保护消息提交
  阶段的隐私。
  最后，利用基于同态加密的数字指纹技术与区块链结合，在
  不依赖可信第三方的情况下保护数据版权。
\end{abstract}

\begin{abstract*}
%  This is a sample document of USTC thesis \LaTeX{} template for bachelor,
%  master and doctor. The template is created by zepinglee and seisman, which
%  orignate from the template created by ywg. The template meets the
%  equirements of USTC theiss writing standards.

%  This document will show the usage of basic commands provided by \LaTeX{} and
%  some features provided by the template. For more information, please refer to
%  the template document ustcthesis.pdf.
Traditional crowdsourcing data transactions rely on a trusted third party, 
and relying on a trusted third party not only significantly increases the cost
but also makes it difficult to prevent collusion to ensure fairness. The emergence
of blockchain and smart contracts provides a decentralized solution to automate
the auction process. However, the existing solutions cannot guarantee the
authenticity of the transaction while choosing the most suitable supplier.
To this end, an auction model using Bayesian Nash equilibrium and smart contract
technology is proposed. First, use Bayesian Nash equilibrium to select the supplier
with the greatest benefit. Secondly, due to the transparency of the blockchain,
in order to satisfy the basic assumption of the static Bayesian Nash equilibrium and 
ensure simultaneous bidding, a two-step message submission algorithm is proposed 
to protect the privacy of the message submission stage. Finally, the digital 
fingerprint technology based on homomorphic encryption is combined with the 
blockchain to protect data copyright without relying on a trusted third party.
\end{abstract*}
